%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% modern themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

\usepackage{import}

% personal data
\name{Juan Pablo}{Ibieta Jimenez} %\title{Physics}                               % optional, remove / comment the line if not wanted
\address{Rua do Matão, Travessa R, 187}{Edifício Ala Central -  331}{CEP 05508-090 -São Paulo-SP}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{(+55)11 9484104565}                   % optional, remove / comment the line if not wanted
%\phone[fixed]{01234 123456}                    % optional, remove / comment the line if not wanted
%\phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not wanted
\email{pibieta@if.usp.br}                               % optional, remove / comment the line if not wanted
%\homepage{www.myname.webs.com}                         % optional, remove / comment the line if not wanted
%\extrainfo{additional information}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle

\section{Summary}

\begin{itemize} 
\item Mathematical Physics Ph. D. candidate at the University of S\~{a}o Paulo;
\item Works in the intersection between Quantum Physics and Mathematics, in particular the so called \emph{Topological phases of matter} since 2012. Since 2017, Data Science and Machine Learning are a main activity;
\item Experience with data visualization, analysis, time series and simulations.
\item Teaches Mathematics and Physics at different levels since 2003; 
\item Passionate about programming, mathematics, science, philosophy and music with strong interpersonal communication skills;
\item Fluency in English, Spanish and Portuguese and Good understanding in French.
\end{itemize} 

\section{Experience}

\vspace{3pt}

\begin{itemize}

\item{\cventry{Aug 2012 -- Present}{Universidade de S\~{a}o Paulo, Math. Physics Department}{Junior Researcher / Teaching Assistant}{S\~{a}o Paulo}{Brazil}{\vspace{1pt} 
\begin{itemize} 
\item Actively collaborating with the Topological Quantum Field Theory lead by Prof. Dr. Paulo Teotônio Sobrinho.
\item Working in Deep Learning solutions for Question/Answer Bots using Natural Language Processing (NLP). Computer Vision for the detection of Astrophysical Objects, in particular using CNNs for this task.
\item Actively colaborating in the Data Science group at the Department.
\item Taught various Physics and Mathematics courses as teaching assistant to engineering and science students at the undergraduate and graduate levels. 
\end{itemize} }}

\vspace{1pt}

\item{\cventry{Jan 2018}{Universidad Mayor de San Andrés, Physics Department}{Visiting Professor}{La Paz}{Bolívia}{\vspace{1pt}
Taught the \emph{Group Theory and Physics} course it the 1st Summer School. 
}}
\vspace{1pt}

\item{\cventry{Jul 2008 -- Dec 2013}{Smarthinking.com / Latinhire.com}{Online Tutor}{La Paz}{Bolivia}{\vspace{1pt} 
\begin{itemize} 
\item Worked as an online tutor of Mathematics and Physics for the Smarthinking.com service through Latinhire.com.
\item Tutoring sessions were mostly in English.
\end{itemize} }}

\vspace{1pt}


\item{\cventry{Feb 2005 -- Aug 2010}{Universidad Mayor de San Andrés, Physics Department}{Junior Researcher / Teaching Assistant}{La Paz}{Bolivia}{\vspace{1pt} 
\begin{itemize} 
\item "Cum Laude" graduation for a small research project on Loop Quantum Gravity.
\item Actively collaborated with the Complex Systems Group.
\item Taught Physics and Mathematics to engineering and science students at the undergraduate and graduate levels. 
\end{itemize} }}


\vspace{1pt}

\end{itemize}


\section{Education}

\vspace{3pt}

\begin{itemize}

\item{\cventry{May 2015 -- Present}{Graduate}{University of Sao Paulo (USP)}{São Paulo, Brazil}{\textit{Ph. D. in Physics}}{Mathematical Physics Department, Physics Institute}}  % arguments 3 to 6 can be left empty

\vspace{1pt}

\item{\cventry{Aug 2012 -- Apr 2015}{Graduate}{University of Sao Paulo (USP)}{São Paulo, Brazil}{\textit{M.Sc. in Physics}}{Mathematical Physics Department, Physics Institute}}

\vspace{1pt}

\item{\cventry{Jul 2011 -- Jan 2012}{Graduate}{Universidad Católica Boliviana - San Pablo (UCB)}{La Paz, Bolivia}{\textit{Diploma on Higher Education}}{Department of Education}}

\vspace{1pt}


\item{\cventry{February 2004 -- July 2010}{Undergraduate}{Universidad Mayor de San Andrés (UMSA)}{La Paz, Bolivia}{\textit{Bachelor in Physics}}{Physics Department}}  % arguments 3 to 6 can be left empty


\end{itemize}
\section{Selected papers}

\vspace{3pt}

\begin{itemize}
\item \textbf{Deformed quantum double realization of the toric code and beyond}. Padmanabhan, P., Ibieta-Jimenez, J. P., Ferreira, M. J. B., and Teotonio-Sobrinho, P. (2016). Annals of Physics, 372, 238-259. https://arxiv.org/abs/1408.2501
\vspace{1pt}
\item \textbf{A Recipe for Constructing Frustration-Free Hamiltonians with Gauge and Matter Fields in One and Two Dimensions}; Ferreira, M. J. B., Ibieta-Jimenez, J. P., Padmanabhan P.  and  Teôtonio-Sobrinho P.; Journal of Physics A: Mathematical and Theoretical 48.48 (2015): 485206, https://arxiv.org/abs/1503.07601
\vspace{1pt}
\item \textbf{Topological Order from a Cohomological and Higher Gauge Theory perspective}; de Almeida, R. C., Ibieta-Jimenez, J. P., Espiro, J. L. and Teotonio-Sobrinho, P. (2017). arXiv preprint arXiv:1711.04186.
\end{itemize}


\section{Technical and Personal skills}

\vspace{4pt}

\begin{itemize}

\item \textbf{Computer / Informatics:} 
\begin{itemize}
\item Proficiency with programming languages, including Python, R, C, C++, Mathematica and Matlab as well as with TeX and LaTeX text processors;
\item Python libraries: Pandas, Numpy, Matplotlib, seaborn, Tensorflow, Keras, scikit-learn, XGBoost, NLTK, spacy, scikit-learn, OpenCV.
\item Web: HTML, CSS, Flask, Django
\item Databases: SQL, MySQL.
\item Proficiency in vector graphic design for illustrating academic texts. 
\end{itemize}

\item \textbf{Personal / Communication Skills:} 

\begin{itemize}
\item Proven skills in innovative problem solving, theoretical research and abstract thinking;
\vspace{1pt}
\item Ability to integrate and lead groups in different contexts and tasks; 
\vspace{1pt}
\item Professional communication skills including fluency in English, Spanish and Portuguese;

\end{itemize}

\end{itemize}
\section{Languages}
\vspace{4pt}
\begin{itemize}
\item{\textbf{Spanish:}} Native Speaker;
\item{\textbf{English:}} Fluent;
\item{\textbf{Portuguese:}} Fluent;
\item{\textbf{French}:} Basic.
\end{itemize}

\section{Events}
\vspace{4pt}
\begin{itemize}
\item{\cventry{Dec 2018}{Instituto de Física Teórica (IFT)- UNESP}{2018 CODATA-RDA School of Research Data Science}{São Paulo}{Brasil}{\vspace{1pt} 
}}
\item{\cventry{Oct 2018}{Instituto de Física Teórica (IFT)- UNESP}{Introduction to quantum computation and simulability}{São Paulo}{Brasil}{\vspace{1pt} 
}}
\item{\cventry{Aug 2018}{Instituto de Física Teórica (IFT)- UNESP}{From Quantum Information to Many-Body Physics and Beyond}{São Paulo}{Brasil}{\vspace{1pt} 
}}
\item{\cventry{May 2018}{Universidad de los Andes}{School on Mathematical Physics: Topological order and beyond}{Bogotá}{Colômbia}{\vspace{1pt} 
}}
\item{\cventry{Feb 2018 - Mar 2018}{Instituto de Física Teórica (IFT)- UNESP}{School on Nonlinear Time Series Analysis and Complex Networks}{São Paulo}{Brasil}{\vspace{1pt} 
}}
\item{\cventry{Sep 2017}{Instituto de Física Teórica (IFT)- UNESP}{Minicourse on Machine Learning for Many-Body Physics}{São Paulo}{Brasil}{\vspace{1pt} 
}}
\item{\cventry{Apr 2017}{Instituto de Física Teórica (IFT)- UNESP}{
School on AdS/CMT Correspondence}{São Paulo}{Brasil}{\vspace{1pt} 
}}
\item{\cventry{Nov 2014}{International Institute of Physics (IIP) - UFRN}{
Group Theory and Knots}{Natal}{Brasil}{\vspace{1pt} 
}}
\item{\cventry{Jul 2010}{Universidad de Buenos Aires (UBA)}{
Quantum Gravity in the Southern Cone V}{Buenos Aires}{Argentina}{\vspace{1pt} 
}}
\end{itemize}


%
%\section{Interests and extra-curricular activity}
%
%\vspace{3pt}
%
%\begin{itemize}
%
%\item{\textbf{Music} 
%\begin{itemize} 
%\item Music passionate and collector.
%\item Amateur electronic music producer.
%\end{itemize}}
%
%\vspace{1pt}
%\item{\textbf{Sports}
%\begin{itemize} 
%\item Currently practicing Running and Calisthenics.
%\item Practiced and played Volleyball for the High-school.
%\item Practiced and played Tennis for almost 10 years.
%\end{itemize}}
%
%\item{\textbf{Gastronomics}
%\begin{itemize} 
%\item Very passionate about cooking and experiencing new food.
%\item Hot pepper appreciator. 
%\end{itemize}}
%
%
%
%%\vspace{1pt}

%\item{\textbf{Sports}
%\begin{itemize} 
%\item Practiced and played Volleyball for the High-school and University team when studying.
%\end{itemize}}

%\end{itemize}

% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}
\nocite{*}
\bibliographystyle{plain}
\bibliography{publications}                        % 'publications' is the name of a BibTeX file

% Publications from a BibTeX file using the multibib package
%\section{Publications}
%\nocitebook{book1,book2}
%\bibliographystylebook{plain}
%\bibliographybook{publications}                   % 'publications' is the name of a BibTeX file
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications}                   % 'publications' is the name of a BibTeX file

%-----       letter       ---------------------------------------------------------

\end{document}


%% end of file `template.tex'.
\grid
